### 2018-11-28 daniel_thesis/para_force_se.tex

\chapter{Parallelisation of the Analytical Forces Induced by Dislocations on Surface Elements}
\label{c:para_f_dln_se}
	%
	\section{Parallelisation on Graphics Processing Units}
	Efficient parallelisation requires \kwd{cma}, which means we have to be extremely careful when mapping CPU memory to device memory. The fact that threads work ``simultaneously'' means that in order to obtain good performance, the data which is to be ``simultaneously'' loaded into each thread must be contiguous. This maximises cache memory use and therefore reduces slow memory fetch operations to global or shared memory.

>>>>

\chapter{Parallelisation of the Analytical Forces Induced by Dislocations on Surface Elements}
\label{c:para_f_dln_se}
	%
	\section{Parallelisation on Graphics Processing Units}
	Efficient parallelisation requires \kwd{cma}, which means we have to be extremely careful when mapping CPU memory to device memory. The fact that threads work ``simultaneously''\footnote{Not quite but essentially simultaneously.} means that in order to obtain good performance, data which is to be ``simultaneously'' loaded into each thread must be contiguous. This maximises cache memory use and therefore reduces slow memory fetch operations to global or shared memory.
